Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-10-08 paper.tex
Added ensemble classifiers figures
Added results of ensemble classifiers

\usepackage{graphics}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}

@@

@@

\begin{table}
\caption{Classification results using basic classifiers (without print-run)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 & kNN  & NB  & J48  & MLP  & SVM\tabularnewline
\hline 
\hline 
$Accuracy$  & 0.69$\pm$0.0026 & 0.67$\pm$0.0008 & 0.7$\pm$0.004 & 0.71$\pm$0.0027 & 0.67$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{L}$  & 0.75$\pm$0.0044 & 0.86$\pm$0.0013 & 0.79$\pm$0.0071 & 0.78$\pm$0.0222 & 0.59$\pm$0.0035\tabularnewline
\hline 
$Precision_{L}$  & 0.78$\pm$0.003 & 0.73$\pm$0.0017 & 0.8$\pm$0.0049 & 0.8$\pm$0.0173 & 0.84$\pm$0.0025\tabularnewline
\hline 
\hline 
$Recall_{M}$  & 0.74$\pm$0.0034 & 0.66$\pm$0.0024 & 0.7$\pm$0.0072 & 0.71$\pm$0.0129 & 0.82$\pm$0.002\tabularnewline
\hline 
$Precision_{M}$  & 0.65$\pm$0.003 & 0.64$\pm$0.0007 & 0.68$\pm$0.0079 & 0.69$\pm$0.007 & 0.59$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{H}$  & 0.59$\pm$0.0047 & 0.53$\pm$0.0022 & 0.6$\pm$0.0099 & 0.65$\pm$0.0346 & 0.55$\pm$0.0016\tabularnewline
\hline 
$Precision_{H}$  & 0.62$\pm$0.0037 & 0.58$\pm$0.0017 & 0.62$\pm$0.0058 & 0.62$\pm$0.0109 & 0.63$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{VH}$  & 0.6$\pm$0.0073 & 0.53$\pm$0.003 & 0.72$\pm$0.0086 & 0.68$\pm$0.0336 & 0.61$\pm$0.0012\tabularnewline
\hline 
$Precision_{VH}$  & 0.79$\pm$0.0071 & 0.81$\pm$0.0032 & 0.74$\pm$0.0072 & 0.77$\pm$0.0212 & 0.78$\pm$0.0028\tabularnewline
\hline 
\end{tabular}
\end{table}

>>>>

\usepackage{graphics,subfigure}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{books_methodology}
\end{center}
\caption{Proposed methodology.}
\label{fig:count}
\end{figure*}

@@

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performes regarding each class. Therefore, precision and recall rates are examined. \\

\begin{table}
\caption{Classification results using basic classifiers (without print-run)}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 & kNN  & NB  & J48  & MLP  & SVM\tabularnewline
\hline 
\hline 
$Accuracy$  & 0.69$\pm$0.0026 & 0.67$\pm$0.0008 & 0.7$\pm$0.004 & 0.71$\pm$0.0027 & 0.67$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{L}$  & 0.75$\pm$0.0044 & 0.86$\pm$0.0013 & 0.79$\pm$0.0071 & 0.78$\pm$0.0222 & 0.59$\pm$0.0035\tabularnewline
\hline 
$Precision_{L}$  & 0.78$\pm$0.003 & 0.73$\pm$0.0017 & 0.8$\pm$0.0049 & 0.8$\pm$0.0173 & 0.84$\pm$0.0025\tabularnewline
\hline 
\hline 
$Recall_{M}$  & 0.74$\pm$0.0034 & 0.66$\pm$0.0024 & 0.7$\pm$0.0072 & 0.71$\pm$0.0129 & 0.82$\pm$0.002\tabularnewline
\hline 
$Precision_{M}$  & 0.65$\pm$0.003 & 0.64$\pm$0.0007 & 0.68$\pm$0.0079 & 0.69$\pm$0.007 & 0.59$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{H}$  & 0.59$\pm$0.0047 & 0.53$\pm$0.0022 & 0.6$\pm$0.0099 & 0.65$\pm$0.0346 & 0.55$\pm$0.0016\tabularnewline
\hline 
$Precision_{H}$  & 0.62$\pm$0.0037 & 0.58$\pm$0.0017 & 0.62$\pm$0.0058 & 0.62$\pm$0.0109 & 0.63$\pm$0.0012\tabularnewline
\hline 
\hline 
$Recall_{VH}$  & 0.6$\pm$0.0073 & 0.53$\pm$0.003 & 0.72$\pm$0.0086 & 0.68$\pm$0.0336 & 0.61$\pm$0.0012\tabularnewline
\hline 
$Precision_{VH}$  & 0.79$\pm$0.0071 & 0.81$\pm$0.0032 & 0.74$\pm$0.0072 & 0.77$\pm$0.0212 & 0.78$\pm$0.0028\tabularnewline
\hline 
\end{tabular}
\label{table:basic_classifiers}
\end{table}

\begin{figure*}[ht]

\centerline{\includegraphics[scale=0.42]{RF}}

\caption{Performance of RF classifier over different number of trees.}
\label{fig:count}
\end{figure*}

\begin{figure*}[ht]
\centerline{
\includegraphics[scale=0.46]{Bagging}}

\caption{Performance of Bagging classifier over different number of iterations.}
\label{fig:count}
\end{figure*}

\begin{figure*}[ht]
\centerline{
\includegraphics[scale=0.46]{Adaboost}
}
\caption{Performance of Adaboost classifier over different number of iterations.}
\label{fig:count}
\end{figure*}

\begin{table}
\caption{Classification results using ensemble classifiers (RF, AdaBoost and Bagging)}
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
 & RF  &  AdaBoost &  Bagging \tabularnewline
\hline 
 \hline $Accuracy$ & 0.741 $\pm$ 0.002 & 0.743 $\pm$ 0.0023 & 0.735 $\pm$ 0.0022 \tabularnewline 
 \hline 
 \hline $Recall_{L}$ & 0.796 $\pm$ 0.0038 & 0.793 $\pm$ 0.0038 & 0.792 $\pm$ 0.0048 \tabularnewline 
 \hline $Precision_{L}$ & 0.823 $\pm$ 0.0035 & 0.827 $\pm$ 0.0032 & 0.814 $\pm$ 0.0043 \tabularnewline 
 \hline 
 \hline $Recall_{M}$ & 0.748 $\pm$ 0.0033 & 0.75 $\pm$ 0.0029 & 0.738 $\pm$ 0.0038 \tabularnewline 
 \hline $Precision_{M}$ & 0.712 $\pm$ 0.0026 & 0.716 $\pm$ 0.0032 & 0.707 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{H}$ & 0.68 $\pm$ 0.0073 & 0.684 $\pm$ 0.0051 & 0.667 $\pm$ 0.0065 \tabularnewline 
 \hline $Precision_{H}$ & 0.666 $\pm$ 0.0037 & 0.667 $\pm$ 0.0029 & 0.663 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{VH}$ & 0.723 $\pm$ 0.0054 & 0.727 $\pm$ 0.0041 & 0.731 $\pm$ 0.0057 \tabularnewline 
 \hline $Precision_{VH}$ & 0.816 $\pm$ 0.0051 & 0.808 $\pm$ 0.0056 & 0.793 $\pm$ 0.0069 \tabularnewline 
\hline 
\end{tabular}
\label{table:basic_classifiers}
\end{table}
